---
title: "Árbol de Navidad"
author: "Antonio Canepa"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Árbol de Navidad
Instrucciones para graficar un árbol de navidad en ggplot2.

El tu tutorial viene de [https://drmowinckels.io/blog/2018/christmas-tree-in-ggplot/](https://drmowinckels.io/blog/2018/christmas-tree-in-ggplot/)

### Carga de paquetes (modo silencio activado)
```{r, message=FALSE, warning=FALSE}
library(tidyverse, quietly = T)
library(gganimate, quietly = T)
```

### The tree cone
First, lest just make a triangle and make it green!

```{r}
cone = data.frame(x = 1:9,
                  y = c(1:5,4:1)) %>% 
  na.omit() %>% 
  arrange(x)

cone %>% 
  ggplot(aes(x=x, y=y)) +
  geom_polygon(fill="#213c18")
```

### Add some fancy stuff

This as actually meant to alter the cone and get the distinct Christmas tree shape, but I couldn’t manage the little “dips” at each branch, the wrong points kept connecting. So it enved up with this more abstract, contemporary thing, which I actually really like!

```{r}
fancy = cone %>% 
  mutate(xoff = ifelse(x<5, x+.4, ifelse(x>5, x-.4, NA))) %>% 
  gather(del, x, contains("x")) %>% 
  mutate(y = ifelse(del=="xoff", y-.1,y)) %>% 
  filter(y>=1) %>% 
  na.omit() %>% 
  select(-del) %>% 
  arrange(y) 

cone %>% 
  ggplot(aes(x=x, y=y)) +
  geom_polygon(fill="#213c18") +
  geom_polygon(data=fancy, fill = "#668c6f")
```

### BAUBLES!
What christmas tree would it be without some baubles! We define some nice christmas’y colours, do some data sample-randomness stuff, and voila!

```{r}
# Define bauble colours
bauble_colours = c("#e5d08f", "#e3d4b6",
                   "#cacbce", "#9c9c9c", "#e1dfdf",
                   "#c94c4c", "#8d1414")

baubles = cone %>% 
  
  # Group by y, nest and make up some random values for x.
  group_by(y) %>% 
  nest() %>% 
  mutate(data =  map(data, ~data.frame(x=seq(min(.$x), max(.$x), by=.1)))) %>% 
  unnest() %>% 
  
  # Group by x, nest and make up some random values for y.
  group_by(x) %>% 
  nest() %>% 
  mutate(data =  map(data, ~data.frame(y=seq(min(.$y), max(.$y), by=.1)))) %>% 
  unnest() %>% 
  ungroup() %>% 
  
  # Give baubles random shapes, sizes and two different colours.
  mutate(col1 = sample(bauble_colours, nrow(.), replace = T),
         col2 = sample(bauble_colours, nrow(.), replace = T),
         shp = sample(1:7, nrow(.), replace = T),
         sz = sample(seq(.5,2,by=.1), nrow(.), replace = T),
         time = sample(seq(.5,1,by=.01), nrow(.), replace = T)
  ) %>%
  rownames_to_column() %>% 
  
  # Grab only 60 baubles
  sample_n(60) %>% 
  
  # Gather the colours into a single column
  gather(dd, cols, contains("col")) %>% 
  mutate(alph = ifelse(dd == "col1", .8, 1))
```

```{r}
cone %>% 
  ggplot(aes(x=x, y=y)) +
  geom_polygon(fill="#213c18") +
  geom_polygon(data=fancy, fill = "#668c6f") +
  geom_point(data = baubles, aes(colour=I(cols), fill=I(cols), 
                                 shape = factor(shp),size=sz), show.legend = F) + 
  scale_shape_manual(values = c(20:25,8))
```

### Add the topper and animate some sparkly!

We need a tree topper, in Norway, we usually add the Christmas star. And then I wanted some ornaments to seemlingly sparkle a little, so we add a small animation too!

```{r}
final_static_tree <- 
  cone %>% 
  ggplot(aes(x=x, y=y)) +
  
  # Cone
  geom_polygon(fill="#213c18") +
  
  # Fancy
  geom_polygon(data=fancy, fill = "#668c6f") +
  
  # Baubles
  # geom_point(data = baubles %>% select(-time), show.legend = F, alpha = .7,
  #            aes(colour=I(cols), fill=I(cols),
  #                shape = factor(shp),size=sz, group=rowname)) +
  geom_point(data = baubles, show.legend = F, alpha = .7,
             aes(colour=I(cols), fill=I(cols),
                 shape = factor(shp),size=sz, group=rowname)) +
  
  # animated baubles!
  geom_point(data = baubles, show.legend = F,
             aes(colour=I(cols), fill=I(cols), alpha=I(alph),
                 shape = factor(shp),size=sz, group=rowname)) + 
  
  # Topper
  geom_point(data=data.frame(x=5, y=5), colour="#e5d08f", size=15, shape=8) +
  scale_shape_manual(values = c(20:25,8)) +
  
  # remove axes etc., and make background black
  theme_void() + 
  theme(plot.background = element_rect(fill="black"), title = element_text(colour="white")) #+
  
  # Animate
  # transition_states(time, transition_length = 10, state_length = 2) + 
  # transition_time(time) + 
  # ease_aes('quadratic-in-out') 

final_static_tree
```

```{r}
ggsave(filename = "Arbol_Navidad.png", plot = final_static_tree, path = paste(getwd(),"/Images" , sep = ""), scale = 0.6, width = 13, height = 20, units = "cm", dpi = 300)
```

