---
title: "Christmas Tree"
author: "Antonio Canepa"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A very ggplot2 Christmas
About a month ago, this classic gem popped up in my Twitter feed. For those unable to view the image, it is a Thanksgiving turkey made completely in ggplot2 by the guys over at is.R. I was so inspired by this plot I decided to see whether I could similarly draw a Christmas tree using only ggplot2:

[Available here](https://t-redactyl.io/blog/2016/12/a-very-ggplot2-christmas.html)

### Your base tree

```{r}
ChristmasTree <- read.csv("https://raw.githubusercontent.com/t-redactyl/Blog-posts/master/Christmas%20tree%20base%20data.csv")

library(ggplot2)

tree <- ggplot() + 
          geom_tile(data = ChristmasTree, aes(x = Tree.X, y = Tree.Y, fill = Tree.Colour)) +       
          scale_fill_identity() + 
          theme_bw() +
          scale_x_continuous(breaks = NULL) + 
          scale_y_continuous(breaks = NULL) +
          labs(x = "", y = "")
tree
```

### Hanging some lights

```{r}
Desired.Lights <- 70
Total.Lights <- sum(round(Desired.Lights * 0.35) + round(Desired.Lights * 0.20) + 
                      round(Desired.Lights * 0.17) + round(Desired.Lights * 0.13) +
                      round(Desired.Lights * 0.10) + round(Desired.Lights * 0.05))

Lights <- data.frame(Lights.X = c(round(runif(round(Desired.Lights * 0.35), 4, 18), 0),
                                       round(runif(round(Desired.Lights * 0.20), 5, 17), 0),
                                       round(runif(round(Desired.Lights * 0.17), 6, 16), 0),
                                       round(runif(round(Desired.Lights * 0.13), 7, 15), 0),
                                       round(runif(round(Desired.Lights * 0.10), 8, 14), 0),
                                       round(runif(round(Desired.Lights * 0.05), 10, 12), 0)))
Lights$Lights.Y <- c(round(runif(round(Desired.Lights * 0.35), 4, 6), 0),
                          round(runif(round(Desired.Lights * 0.20), 7, 8), 0),
                          round(runif(round(Desired.Lights * 0.17), 9, 10), 0),
                          round(runif(round(Desired.Lights * 0.13), 11, 12), 0),
                          round(runif(round(Desired.Lights * 0.10), 13, 14), 0),
                          round(runif(round(Desired.Lights * 0.05), 15, 17), 0))
Lights$Lights.Colour <- c(round(runif(Total.Lights, 1, 4), 0))
```


```{r}
tree <- tree +
          geom_point(data = Lights, aes(x = Lights.X, y = Lights.Y, alpha = Lights.Colour),
                     colour = "lightgoldenrodyellow", shape = 16) +
          theme(legend.position = "none")
tree
```

### Adding the baubles
```{r}
Baubles <- data.frame(Bauble.X = c(6, 9, 15, 17, 5, 13, 16, 7, 10, 14, 7, 9, 11, 
                                   14, 8, 14, 9, 12, 11, 12, 14, 11, 17, 10))
Baubles$Bauble.Y <- c(4, 5, 4, 4, 5, 5, 5, 6, 6, 6, 8, 8, 8, 8, 10,
                      10, 11, 11, 12, 13, 10, 16, 7, 14)
Baubles$Bauble.Colour <- factor(c(1, 2, 2, 3, 2, 3, 1, 3, 1, 1, 1, 2, 1, 2,
                                  3, 3, 2, 1, 3, 2, 1, 3, 3, 1))
Baubles$Bauble.Size <- c(1, 3, 1, 1, 2, 1, 2, 2, 2, 1, 1, 1, 3, 3, 3,
                         2, 3, 1, 1, 2, 2, 3, 3, 2)
```


```{r}
tree <- tree + 
          geom_point(data = Baubles, aes(x = Bauble.X, y = Bauble.Y, 
                                         colour = Bauble.Colour, size = Bauble.Size),
                     shape = 16) +
          scale_colour_manual(values = c("firebrick2", "gold", "dodgerblue3")) +
          scale_size_area(max_size = 12)
tree
```

### Decorating the presents

```{r}
tree <- tree +
          geom_segment(aes(x = 2.5, xend = 4.5, y = 1.5, yend = 1.5), colour = "blueviolet", size = 2) +
          geom_segment(aes(x = 5.5, xend = 8.5, y = 1.5, yend = 1.5), colour = "dodgerblue3", size = 2) +
          geom_segment(aes(x = 13.5, xend = 16.5, y = 1.5, yend = 1.5), colour = "blueviolet", size = 2) +
          geom_segment(aes(x = 17.5, xend = 19.5, y = 1.5, yend = 1.5), colour = "dodgerblue3", size = 2) +
          geom_segment(aes(x = 3.5, xend = 3.5, y = 0.5, yend = 2.5), colour = "blueviolet", size = 2) +
          geom_segment(aes(x = 7.0, xend = 7.0, y = 0.5, yend = 2.5), colour = "dodgerblue3", size = 2) +
          geom_segment(aes(x = 15.0, xend = 15.0, y = 0.5, yend = 2.5), colour = "blueviolet", size = 2) +
          geom_segment(aes(x = 18.5, xend = 18.5, y = 0.5, yend = 2.5), colour = "dodgerblue3", size = 2)
tree
```

### Writing a greeting

```{r, message=FALSE, warning=FALSE}
library(extrafont)
#font_import()
loadfonts()
```


```{r}
tree_eng <- tree +
          annotate("text", x = 11, y = 20, label = "Merry Christmas!", 
                   family = "Georgia", size = 12)
tree_eng
```

```{r}
tree_sp <- tree +
          annotate("text", x = 11, y = 20, label = "¡Felíz Navidad!", 
                   family = "Georgia", size = 12)
tree_sp
```

```{r, purl=FALSE, eval=FALSE}
ggsave(filename ='Christmas_tree.png' , plot = tree_eng, path = paste(getwd(), "/Images", sep = ""), scale = , width = 20, height = 25, units = "cm", dpi = 300)
```


```{r, purl=FALSE, eval=FALSE}
ggsave(filename ='Arbol_Navidad_2.png' , plot = tree_sp, path = paste(getwd(), "/Images", sep = ""), scale = , width = 20, height = 25, units = "cm", dpi = 300)
```
